resistanceModelNotesAndy

### 2016-02-01 effectOfIndividualInputs.Rmd
hunting anomaly

## In the following plots all inputs are plotted individually, the points are coloured by exposure, which allows us to see that, even as other inputs change, low times to resistance are associated with high exposure.
```{r, eval=TRUE, echo=FALSE}

@@

## Looking more closely at effect of the ratio between the level of resistance to the first insecticide divided by that of the second one. Restricting the x axis to lower values.
```{r, eval=TRUE, echo=FALSE}

@@

#trying a PRCC analysis using the package sensitivity
```{r, eval=TRUE, echo=FALSE}

@@

  #first attempt
  by_strategy <- ggInsOuts[ggInsOuts$strategy=='insecticide 1',]

@@

  to_plot <- pcc_res$PRCC
  to_plot$test <- c(1:nrow(to_plot))
  to_plot$names <- rownames(to_plot)

  ggplot( to_plot, aes_string(x='names',y='original') ) + 
           geom_point(shape=3) +
           theme(axis.text.x = element_text(angle = 45))

@@

>>>>

## In the following plots all inputs are plotted individually, the points are coloured by exposure, which allows us to see that, even as other inputs change, low times to resistance are associated with high exposure.
```{r, eval=TRUE, echo=FALSE, fig.height=3.5}

@@

## Looking more closely at effect of the ratio between the level of resistance to the first insecticide divided by that of the second one. Restricting the x axis to lower values.
```{r, eval=TRUE, echo=FALSE, warning=FALSE}

@@

#trying a PRCC analysis using the package sensitivity
```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=3.5}

@@

  strategies <- unique(ggInsOuts$strategy)

  for(strategy in strategies)
  {

    by_strategy <- ggInsOuts[ggInsOuts$strategy==strategy,]

@@

    to_plot <- pcc_res$PRCC
    #rename column 1 from 'original to PRCC
    names(to_plot)[1] <- 'PRCC'
    to_plot$inputs <- rownames(to_plot)

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             ylim(-1,1) +
             ggtitle(paste(strategy,"PRCC")) +
             xlab(NULL)
          )
  }

@@

```{r, eval=FALSE, echo=FALSE, warning=FALSE, fig.height=3.5}

#trying to find apparent anomaly in PRCC analysis
#what causes correctMixDeployProp to get a high PRCC score for I1 & 2 when its not used in those runs ??

tstI1 <- round(listOutI1$input,3)
tstMix <- round(listOutMix$input,3)
tstDif <- round(tstMix - tstI1,3)
